Precise Weed and Maize Classification through Convolutional Neuronal Networks

### 2017-08-17 PaperBCJ.tex
Corrections of Tables

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{array}
\usepackage{filecontents}
\usepackage{caption}
\usepackage[noadjust]{cite}
\captionsetup[table]{position=bottom} %% or below

@@

@@

A Raspberry Pi 3 with a V2.1 Pi camera for image acquisition was used for the training and image-capturing stages. The system was configured to obtain a video at a resolution of 1280x720 pixels in order to get more detail in the segmented images. Due to the popularity of GPU computing for its advantages in the development of models of Convolutional Neural Networks, such as a better processing speed, it was necessary to consider hardware compatible with parallel computing devices such as the Graphic Cards manufactured by NVIDIA. These cards have the advantage of a superior processing speed compared to a CPU in order to optimize image-processing time and deep learning Model's training process, thus the selected device was a computer with a Nvidia graphics card GTX950M. Also, it was necessary to consider the use of a Core i7 2.7 Ghz CPU of 8 cores and the CPU of the Raspberry Pi 3, with an ARM Cortex-A53, 1.2GHz, and 4 cores, in order to test their performance for a future application in an independent mobile system that could be implemented in an embedded system. The hardware chosen will be tested to classify images, in each classification a measurement of the processing time will be taken to later on analyze if the hardware can process information in real time. 
\\

@@

Also, the use of Linux OS in the development stages was important due to its light operating system and free OS which is also fully compatible with OpenCV. The computer used in the project worked with Ubuntu Linux 16.04 due to its official support to CUDA, Caffe and OpenCV. Likewise, PIXEL Distribution derived from Debian Linux was used in Raspberry Pi for acquiring images and testing the CNN classification performance.
\\

@@

	\begin{figure}[h]
	\centering
	\includegraphics[width=3.2in]{entradamaiz}
	\caption{Crops chosen to obtain samples, it is easy to discrimante weed from maize}
	\label{figure1}
	\end{figure}
\begin{comment}
Tambien fue necesario obtener imagenes de las malas hierbas mas comunes en los campos de maiz de Pillaro, para permitir a la Red discrimiar entre las dos clases definidas en el Dataset.
\end{comment}

Also, it was necessary to obtain images of the most common weed plants found in maize crops in P\'illaro, in order to allow the network to discriminate between maize and weeds. \\
\begin{comment}
Entonces, a traves de un proceso de procesamiento digital de imagenes, como primera fase, la imagen fue normalizada en su canal verde, esto mejora la deteccion del color verde porque elimina las luces y las sombras de la imagen, despues extrajimos el color verde de la imagen con la ecuacion descrita opr Wang, Men, Luo and Mei, para obtener una imagen final en escala de grises, despues se aplico una Umbralizacion de OTSU para obtener una mascara binaria 
\end{comment}

Then, through a first-stage digital image processing procedure, the images were normalized in its green channel. This was done in order to improve green color detection based on the elimination of light and shadow in the images. Later, the green color was extracted from the images to obtain a grayscale equivalent; this was done through the following equation described by Wang, Meng, Luo and Mei \cite{wang2013path}. Following, an OTSU Thresholding was applied to the grayscale images in order to obtain a binary mask. 
\begin{equation}
	S = 2*G - R - B
\end{equation} 
\begin{comment}
Despues de la imagen fue segmentada, para diferenciarla del suelo y otros elementos que no sean plantas, las imagenes originales fueron enmascaradas con la mascara binaria para proveer al Dataset caracteristicas de Color del Maiz y de la Mala Hierba. Una vez ue las imagenes segmentedas fueron obtenidas, removimos aquellas que tenian una resolucion menor a 64x64 pixeles debido a que son mas pequenhas que el tamanho de entrada de la red, ademas no es conveniente procesarlas debido a que su area total es mucho mas pequenha que la de las muestras de maiz, las cuales son el proposito de este documento, despues las imagenes se almacenan en un formato Png. El proceso se ilustra de mejor manera en la siguiente figura.
\end{comment}

Afterwards, the images were segmented in order to differentiate them from the soil and other non-plant elements. Original images were masked to provide the dataset with color features of maize and weed plants. Once the segmented images were obtained, the files that had a resolution lower than 64x64 pixels were removed because its size was smaller than the size of the network input layer. Besides, the processing of these small images was not convenient since its total area was much smaller than the maize sample images. Following, the images were saved in a png format. The entire process described before is illustrated in Fig. \ref{figure2}. \\

@@

It should be noted that samples were manually labeled into two classes; maize and weed, making sure that the images are not repeated. In the following image, final results of the processed images that conform the dataset are shown on the figure \ref{figure3}.\\

	\begin{figure}[h]
	\centering
	\includegraphics[width=2.5in]{im1}
	\caption{ Segmented and Masked images of dataset Above: Weed, Below: Maize}
	\label{figure3}
	\end{figure}

@@

For the validation phase, a fifth part of the total image set of each class was chosen, resulting in the following chart with the dataset distribution.\\

\begin{table}[h!]
\renewcommand{\arraystretch}{1.3}
\caption{DATASET DISTRIBUTION OF EACH CLASS}
\label{table:1}
\centering
\begin{tabular}{| c c c c c |} 
 \hline
 \textbf{Phase} & \textbf{Train} & \textbf{Validation} &\textbf{Test} & \textbf{Total} \\ [1ex] 
 \hline
 Maize & 25695 & 8325 & 202 & 34222 \\ 
 Weed & 8560 & 2000 & 202 & 10762\\ 
 \hline
\end{tabular}

\end{table}

@@

One of the characteristics of CNN is these have multiple architectures, each architecture can reach different results depending on the application. For the present document four CNN architectures have been considered. Two arquitectures were chosen from the Caffe Zoo Model(a free resource provided by Caffe Developers), LeNet and AlexNet. Also, Potena and Nardi\cite{potena2016fast} used two additional types of architectures, sNET and cNET, which sucessfully proved an aceptable performance in plants and crop identification processes. With the four Nets chosen, each one was trained with the same solver of type Adam and with the same dataset. The training results are shown on table \ref{table:2}. \\
\begin{table}[h!]
\centering
\begin{tabular}{|l c c c c|} 
 \hline
 \textbf{Parameters }& \textbf{LeNet} & \textbf{AlexNet} & \textbf{cNET} & \textbf{sNET} \\ [0.75ex] 
 \hline
 Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
 Layers numbers & 9 & 11 & 8 & 4\\
 Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
 Iterations & 3000 & 3000 & 3000 & 3000 \\ 
 Accuracy(\%) & 86.48 & 93.86 & 96.4 & 80.4 \\
 Loss(\%) & 32.80 & 15.32 & 13.72 & 15.32 \\ [1ex] 
 \hline 
\end{tabular}
\caption{Comparison of the 4 types of CNN}
\label{table:2}
\end{table}

@@

Although results given by this type of network are excellent, one of the main purposes of this paper is the implementation of a real time system. The number of parameters to be computed by the selected network were numerous, so it was necessary to make network modifications in order to improve its processing speed. To achieve this, it was necessary to reduce the number of filters of cNET from 64 to 16. This final number of filters used in the network was selected because this is the minimum number of filters that maintain an acceptable training accuracy. \\

\begin{table}[h!]
\centering
\begin{tabular}{|l c c |} 
 \hline
 \textbf{Parameters} & \textbf{cNET 16 filters} & \textbf{cNET 64 filters} \\ [0.75ex] 
 \hline
 Number of parameters & 1651376 & 6421568 \\ 
 Iterations & 9000 & 9000 \\ 
 Accuracy(\%) & 97.26 & 96.40 \\
 Loss(\%) & 8.39 & 14.48 \\ [1ex] 
 \hline 
\end{tabular}
\caption{Comparison between cNET of 16 and 64 filters}
\label{table:3}
\end{table}

@@

In the training graph shown below, the final net accuracy result can be appreciated; 9000 iterations were necessary to reduce the loss value to its minimum and the architecture shows that it can reach an acceptable accuracy within few iterations. Note that by reducing the number of filters the network gained accuracy because the dataset does not have too many features to process, so the network obtained a better solution with a fewer number of parameters. \\

@@

For this stage, another dataset was considered with 202 images of maize plants in stage V3-V7 and 202 images of weeds, obtained in different maize crops than the ones used for gathering the training dataset images. Ten measurements of the mean classification time of the test dataset were obtained for each one of the different hardwares previously selected to run performance tests. Classification tests were started with Caffe in vanilla version. The obtained results were compared between cNET arquitecture with 64 and 16 filters, these are shown on Table \ref{table:4}.\\

\begin{table}[h!]
\centering
\begin{tabular}{|p{1.1cm}|p{1.5cm}|p{1.5cm}|p{2.1cm}|} 
 \hline
 \multicolumn{4}{ |c| }{\textbf{GPU}} \\
 \hline
 \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image} \\ 
 \hline 
 64 Filters & 95.05\% & 74.75\% & 2.34 ms \\ [0.75ex]
 \hline
 16 Filters & 92.08\% & 89.11\% & 951 $\mu$s \\ [0.75ex]
 \hline
 \multicolumn{4}{ |c| }{\textbf{CPU}} \\
 \hline
 \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image} \\ 
 \hline 
 64 Filters & 95.05\% & 74.75\% & 51.6 ms \\ [0.75ex]
 \hline
 16 Filters & 92.08\% & 89.11\% & 17.23 ms \\ [0.75ex]
 \hline
 \multicolumn{4}{ |c| }{\textbf{CPU Raspberry Pi 3}} \\
 \hline
 \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image} \\
 \hline 
 64 Filters & 95.05 \% & 74.75\% & 615 ms \\ [0.75ex]
 \hline
 16 Filters & 92.08\% & 89.11\% & 161 ms \\ [0.75ex]
 \hline
\end{tabular}
\caption{Test with the three types of Hardware}
\label{table:4}
\end{table}

@@

The results shown previously are not definitive because Caffe has ways to optimize image dataset classification. Multithreading was applied to this research project with the help of the mathematical software OpenBLAS. Also, batching was used to classify each class dataset in a single forward pass. For each hardware, Caffe was recompiled with OpenBLAS instead of Atlas. In the program with cNET of 16 filters, all images were entered in a vector to be classified in an only batch per each class. Also, OpenBLAS was configured to use the 4 cores of each CPU hardware to obtain even results among these two devices. Since GPU has thousands of cores, this test could not be configured under the same restriction for this device. The obtained results are the following. \\

\begin{table}[h!]
\centering
\begin{tabular}[c c c c]{|p{2.2 cm}|p{1.1cm}|p{1.1cm}|p{2.4cm}|} 
 \hline
 \textbf{Hardware } & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image}\\ 
 \hline 
 GPU & 92.08\% & 89.11\% & 1.58 ms \\ [0.95ex]
 \hline
 CPU & 92.08\% & 89.11\% & 10.92 ms \\ [0.95ex]
 \hline
 CPU(Raspberry Pi) & 92.08\% & 89.11\% & 150.8 ms \\ [0.95ex]
 \hline
\end{tabular}
\caption{Test of cNET 16 filters with optimized software}
\label{table:5}
\end{table}

@@

The results show that for the GPU, classification time has increased by 66 \%, mainly because the OpenBLAS Library makes an extensive use of the CPU threads, 
causing some parameters to be computed in the CPU in stead of the GPU, thus making the process slower. For the CPU the results are better because the operations are executed using each of the four cores, for this case a decrease in time of 22\% was obtained. Finally, the result for the Raspberry Pi CPU was a time decrease of 6.3 \%.\\

\begin{comment}	
Ahora para comparar todos estos resultados tomando en cuenta que una imagen capturada por la camara a una altura de 1,5 m puede enfocar un aproximado de 6 plantas de maiz, y segun la cantidad de mala hierba, se considerara un promedio de 12 plantas, dando un total de 18 plantas aproximadamente. Con esto se analiza cuantos frames por segundo seria lo adecuado para la adquisicion de imagenes.
\end{comment}	
Lastly, an image captured by the camera at a height of 1.5 m can focus an approximate 6 plants of maize. Taking into account the number of weeds, an average of 12 plants can show up in the image. The total number of plants per image would round 18 plants considering maize and weeds as well. This aids to determine how many frames per second would be appropriate for the acquisition of images.\\

For the estimation of the frames per second for each device, its optimal configuration was considered. The GPU classification time during the test without multithreading was considered for this device. For the CPU and the Raspberry Pi CPU, the results for classification time in the multithreading tests were considered. The devices that showed a realistic number of frames per second are the GPU and the CPU, while the Raspberry Pi CPU did not obtain an achievable rate.\\

\begin{table}[h!]
\centering
\begin{tabular}[c c c c]{|p{1.1 cm}|p{1.7cm}|p{1.7cm}|p{2.0cm}|} 
 \hline
 \textbf{Parameter} &\textbf{GPU(Without Threading) } & \textbf{CPU with Threading} & \textbf{Raspberry Pi 3 with Threading} \\ 
 \hline 
 Time(s) & 0.0171 & 0.196 & 2.714 \\ [0.95ex]
 \hline
 FPS & 58.47 & 5.08 & 0.36 \\ [0.95ex]
 \hline
\end{tabular}
\caption{Test of a complete image and the frames per second}
\label{table:5}
\end{table}

@@

The use of Multithreading and Batching through the library OpenBLAS is very beneficial in the case of using CPU, increasing the speed of processing in the percentage higher than 20 \%. However with the Rasberry pi, a minimum improvement was obtained, instead the use of GPU was prejudicial because it causes the speed to be reduced considerably. \\

@@

In the case of implementing the algorithm in an embedded system, it is not recommended to work with a processor like Raspberry Pi 3, because it has a very slow processing because the frames per second needed to analyze the images is significantly low, So you should choose a card that has GPU, without the need for Multithreading and Batching. \\

>>>>

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{array}
\usepackage{filecontents}
%\usepackage[noadjust]{cite}

@@

\IEEEoverridecommandlockouts
\IEEEpubid{\makebox[\columnwidth]{\textbf{978-1-5386-3894-1/17/\$31.00~\copyright{}2017 IEEE} \hfill} \hspace{\columnsep}\makebox[\columnwidth]{ }}

@@

A Raspberry Pi 3 with a V2.1 Pi camera for image acquisition was used for the training and image-capturing stages. The system was configured to obtain a video at a resolution of 1280x720 pixels in order to get more detail in the segmented images. Due to the popularity of GPU computing for its advantages in the development of models of Convolutional Neural Networks, such as a better processing speed, it was necessary to consider hardware compatible with parallel computing devices such as the Graphic Cards manufactured by NVIDIA. These cards have the advantage of a superior processing speed compared to a CPU in order to optimize image-processing time and deep learning Model's training process, thus the selected device was a computer with a Nvidia graphics card GTX950M. Also, it was necessary to consider the use of a Core i7 2.7 Ghz CPU of 8 cores and the CPU of the Raspberry Pi 3, with an ARM Cortex-A53, 1.2GHz, and 4 cores, in order to test their performance for a future application in an independent mobile system that could be implemented in an embedded system. The hardware chosen will be tested to classify images, in each classification a measurement of the processing time will be taken to later on \textbf{(revisar)} analyze if the hardware can process information in real time. 
\\

@@

Also, the use of Linux OS in the development stages was important due to its light operating system and free OS which is also fully compatible with the software chosen. The computer used in the project worked with Ubuntu Linux 16.04 due to its official support to CUDA, Caffe and OpenCV. Likewise, PIXEL Distribution derived from Debian Linux was used in Raspberry Pi for acquiring images and testing the CNN classification performance.
\\

@@

	\begin{figure}[h!]
	\centering
	\includegraphics[width=3.2in]{entradamaiz}
	\caption{Crops chosen to obtain samples, it is easy to discrimante weed from maize}
	\label{figure1}
	\end{figure}

\begin{comment}
Tambien fue necesario obtener imagenes de las malas hierbas mas comunes en los campos de maiz de Pillaro, para permitir a la Red discrimiar entre las dos clases definidas en el Dataset.
\end{comment}

Also, it was necessary to obtain images of the most common weed plants found in maize crops in P\'illaro, in order to allow the network to discriminate between maize and weeds. \\

\begin{comment}
Entonces, a traves de un proceso de procesamiento digital de imagenes, como primera fase, la imagen fue normalizada en su canal verde, esto mejora la deteccion del color verde porque elimina las luces y las sombras de la imagen, despues extrajimos el color verde de la imagen con la ecuacion descrita opr Wang, Men, Luo and Mei, para obtener una imagen final en escala de grises, despues se aplico una Umbralizacion de OTSU para obtener una mascara binaria 
\end{comment}

Then, through a first-stage digital image processing procedure, the images were normalized in its green channel. This was done in order to improve green color detection based on the elimination of light and shadow in the images. Later, the green color was extracted from the images to obtain a grayscale equivalent; this was done through the following equation described by Wang, Meng, Luo and Mei \cite{wang2013path}. Following, an OTSU Thresholding was applied to the grayscale images in order to obtain a binary mask. 
\begin{equation}
	S = 2*G - R - B
\end{equation}

\begin{comment}
Despues de la imagen fue segmentada, para diferenciarla del suelo y otros elementos que no sean plantas, las imagenes originales fueron enmascaradas con la mascara binaria para proveer al Dataset caracteristicas de Color del Maiz y de la Mala Hierba. Una vez ue las imagenes segmentedas fueron obtenidas, removimos aquellas que tenian una resolucion menor a 64x64 pixeles debido a que son mas pequenhas que el tamanho de entrada de la red, ademas no es conveniente procesarlas debido a que su area total es mucho mas pequenha que la de las muestras de maiz, las cuales son el proposito de este documento, despues las imagenes se almacenan en un formato Png. El proceso se ilustra de mejor manera en la siguiente figura.
\end{comment}

Afterwards, the images were segmented in order to differentiate them from the soil and other non-plant elements. Original images were masked to provide the dataset with color features of maize and weed plants. Once the segmented images were obtained, the files that had a resolution lower than 64x64 pixels were removed because its size was smaller than the size of the network input layer. Besides, the processing of these small images was not convenient since its total area was much smaller than the maize sample images. Following, the images were saved in a png format. The entire process described before is illustrated in Fig. \ref{figure2}.

@@

It should be noted that samples were manually labeled into two classes; maize and weed, making sure that the images are not repeated. In the following image, final results of the processed images that conform the dataset are shown on the Fig. \ref{figure3}.\\

	\begin{figure}[h]
	\centering
	\includegraphics[width=2.5in]{im1}
	\caption{Segmented and Masked images of dataset Above: Weed, Below: Maize}
	\label{figure3}
	\end{figure}

@@

For the validation phase, a fifth part of the total image set of each class was chosen, resulting in the following Table \ref{table:1} with the dataset distribution.

\begin{table}[h!]
\renewcommand{\arraystretch}{1.3}
\caption{Dataset distribution of each class}
\label{table:1}
\centering
\begin{tabular}{| c c c c c |} 
 \hline
 \textbf{Phase} & \textbf{Train} & \textbf{Validation} &\textbf{Test} & \textbf{Total} \\ [1ex] 
 \hline
 Maize & 25695 & 8325 & 202 & 34222 \\ 
 Weed & 8560 & 2000 & 202 & 10762\\ 
 \hline
\end{tabular}
\end{table}

@@

One of the characteristics of CNN is these have multiple architectures, each architecture can reach different results depending on the application. For the present document four CNN architectures have been considered. Two arquitectures were chosen from the Caffe Zoo Model(a free resource provided by Caffe Developers), LeNet and AlexNet. Also, Potena and Nardi\cite{potena2016fast} used two additional types of architectures, sNET and cNET, which sucessfully proved an aceptable performance in plants and crop identification processes. With the four Nets chosen, each one was trained with the same solver of type Adam and with the same dataset. The training results are shown on Table \ref{table:2}. \\
\begin{table}[h!]
\centering
\renewcommand{\arraystretch}{1.2}
\caption{Comparison of the 4 types of CNN}
\label{table:2}
\begin{tabular}{|l c c c c|} 
 \hline
 \textbf{Parameters }& \textbf{LeNet} & \textbf{AlexNet} & \textbf{cNET} & \textbf{sNET} \\ [0.75ex] 
 \hline
 Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
 Layers numbers & 9 & 11 & 8 & 4\\
 Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
 Iterations & 3000 & 3000 & 3000 & 3000 \\ 
 Accuracy(\%) & 86.48 & 93.86 & 96.4 & 80.4 \\
 Loss(\%) & 32.80 & 15.32 & 13.72 & 15.32 \\ [1ex] 
 \hline 
\end{tabular}
\end{table}

@@

Although results given by this type of network are excellent, one of the main purposes of this paper is the implementation of a real time system. The number of parameters to be computed by the selected network were numerous, so it was necessary to make network modifications in order to improve its processing speed. To achieve this, it was necessary to reduce the number of filters of cNET from 64 to 16. This final number of filters used in the network was selected because this is the minimum number of filters that maintain an acceptable training accuracy. The results of the experiment are shown in the Table \ref{table:3} \\

\begin{table}[h]
\centering
\renewcommand{\arraystretch}{1.2}
\caption{Comparison between cNET of 16 and 64 filters}
\label{table:3}
\begin{tabular}{|l c c |} 
 \hline
 \textbf{Parameters} & \textbf{cNET 16 filters} & \textbf{cNET 64 filters} \\ [0.75ex] 
 \hline
 Number of parameters & 1651376 & 6421568 \\ 
 Iterations & 9000 & 9000 \\ 
 Accuracy(\%) & 97.26 & 96.40 \\
 Loss(\%) & 8.39 & 14.48 \\ [1ex] 
 \hline 
\end{tabular}
\end{table}

@@

In the training graph shown in Fig. \ref{figure5}, the final net accuracy result can be appreciated; 9000 iterations were necessary to reduce the loss value to its minimum and the architecture shows that it can reach an acceptable accuracy within few iterations. Note that by reducing the number of filters the network gained accuracy because the dataset does not have too many features to process, so the network obtained a better solution with a fewer number of parameters. \\

@@

For this stage, another dataset was considered with 202 images of maize plants in stage V3-V7 and 202 images of weeds, obtained in different maize crops than the ones used for \textbf{mejorar} gathering the training dataset images. Ten measurements of the mean classification time of the test dataset were obtained for each one of the different hardwares previously selected to run performance tests. Classification tests were started with Caffe in vanilla version. The obtained results were compared between cNET arquitecture with 64 and 16 filters, these are shown on Table \ref{table:4}.\\

\begin{table}[h]
\centering
\renewcommand{\arraystretch}{1.2}
\caption{Test with the three types of Hardware}
\label{table:4}
\begin{tabular}{|p{1.1cm}|p{1.5cm}|p{1.5cm}|p{2.1cm}|} 
 \hline
 \multicolumn{4}{ |c| }{\textbf{GPU}} \\
 \hline
 \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image} \\ 
 \hline 
 64 Filters & 95.05\% & 74.75\% & 2.34 ms \\ [0.75ex]
 \hline
 16 Filters & 92.08\% & 89.11\% & 951 $\mu$s \\ [0.75ex]
 \hline
 \multicolumn{4}{ |c| }{\textbf{CPU}} \\
 \hline
 \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image} \\ 
 \hline 
 64 Filters & 95.05\% & 74.75\% & 51.6 ms \\ [0.75ex]
 \hline
 16 Filters & 92.08\% & 89.11\% & 17.23 ms \\ [0.75ex]
 \hline
 \multicolumn{4}{ |c| }{\textbf{CPU Raspberry Pi 3}} \\
 \hline
 \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image} \\
 \hline 
 64 Filters & 95.05 \% & 74.75\% & 615 ms \\ [0.75ex]
 \hline
 16 Filters & 92.08\% & 89.11\% & 161 ms \\ [0.75ex]
 \hline
\end{tabular}
\end{table}

@@

The results shown previously are not definitive because Caffe has ways to optimize image dataset classification. Multithreading was applied to this research project with the help of the mathematical software OpenBLAS. Also, batching was used to classify each class dataset in a single forward pass. For each hardware, Caffe was recompiled with OpenBLAS instead of Atlas. In the program with cNET of 16 filters, all images were entered in a vector to be classified in an only batch per each class. Also, OpenBLAS was configured to use the 4 cores of each CPU hardware to obtain even results among these two devices. Since GPU has thousands of cores, this test could not be configured under the same restriction for this device. The obtained results are the shown in Table \ref{table:5}.

\begin{table}[h!]
\centering
\renewcommand{\arraystretch}{1.2}
\caption{Test of cNET 16 filters with optimized software}
\label{table:5}
\begin{tabular}[c c c c]{|p{2.2 cm} p{1.1cm} p{1.1cm} p{2.4cm}|} 
 \hline
 \textbf{Hardware } & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification/image}\\ 
 \hline 
 GPU & 92.08\% & 89.11\% & 1.58 ms \\ [0.95ex]
 CPU & 92.08\% & 89.11\% & 10.92 ms \\ [0.95ex]
 CPU(Raspberry Pi) & 92.08\% & 89.11\% & 150.8 ms \\ [0.95ex]
 \hline
\end{tabular}
\end{table}

@@

The results show that for the GPU, classification time has increased by 66\%, mainly because the OpenBLAS Library makes an extensive use of the CPU threads, causing some parameters to be computed in the CPU instead of the GPU, thus making the process slower. For the CPU the results are better because the operations are executed using each of the four cores, for this case a decrease in time of 22\% was obtained. Finally, the result for the Raspberry Pi CPU was a time decrease of 6.3 \%.\\

\begin{comment}	
Ahora para comparar todos estos resultados tomando en cuenta que una imagen capturada por la camara a una altura de 1,5 m puede enfocar un aproximado de 6 plantas de maiz, y segun la cantidad de mala hierba, se considerara un promedio de 12 plantas, dando un total de 18 plantas aproximadamente. Con esto se analiza cuantos frames por segundo seria lo adecuado para la adquisicion de imagenes.
\end{comment}	
Lastly, an image captured by the camera at a height of 1.5 m can focus an approximate 6 plants of maize. Taking into account the number of weeds, an average of 12 plants can show up in the image. The total number of plants per image would round 18 plants considering maize and weeds as well. This aids to determine how many frames per second would be appropriate for the acquisition of images. \\

For the estimation of the frames per second for each device, its optimal configuration was considered. The GPU classification time during the test without multithreading was considered for this device. For the CPU and the Raspberry Pi CPU, the results for classification time in the multithreading tests were considered. The devices that showed a realistic number of frames per second are the GPU and the CPU, while the Raspberry Pi CPU did not obtain an achievable rate like it\'s shown in Table \ref{table:6}.\\

\begin{table}[h!]
\centering
\renewcommand{\arraystretch}{1.2}
\caption{Test of a complete image and the frames per second}
\label{table:6}
\begin{tabular}[c c c c]{|p{1.1 cm} p{1.7cm} p{1.7cm} p{2.0cm}|} 
 \hline
 \textbf{Parameter} &\textbf{GPU(Without Threading) } & \textbf{CPU with Threading} & \textbf{Raspberry Pi 3 with Threading} \\ 
 \hline
 Time(s) & 0.0171 & 0.196 & 2.714 \\ [0.95ex]
 FPS & 58.47 & 5.08 & 0.36 \\ [0.95ex]
 \hline
\end{tabular}
\end{table}

@@

The use of Multithreading and Batching through the library OpenBLAS is very beneficial in the case of using CPU, increasing the speed of processing in the percentage higher than 20 \%. However with the Rasberry Pi, a minimum improvement was obtained, instead the use of GPU was prejudicial because it causes the speed to be reduced considerably. \\

@@

In the case of implementing the algorithm in an embedded system, it is not recommended to work with a processor like Raspberry Pi 3 for now(due they are promising advances in external Deep Lerning devices for embedded systems such as the Intel Movidius Neural Compute Stick), because it has a very slow processing because the frames per second needed to analyze the images is significantly low, so you should choose a card that has GPU, without the need for Multithreading and Batching. \\
